Blame and Coercion: Together Again for the Second Time

### 2019-10-10 paper.tex
minor fixes

\begin{figure}
	\fbox{$ c \fatsemi^\ell c = c $}
	\[ 
	\begin{array}{rclclr}

@@

	\fbox{$ m \fatsemi^\ell (m,t) = (m,t) $}
	\[ 
	\begin{array}{rclclr}
	\comprule{\POOunit}{(\POOunit,t)}{
		(\POOunit,t)
	}{}
	\comprule{\POOfun{c_1}{c_2}}{(\POOfun{c_3}{c_4},t)}{
		(\POOfun{c_3 \fatsemi^{\ell} c_1}{c_2 \fatsemi^\ell c_4},t)
	}{}
	\comprule{\POOprod{c_1}{c_2}}{(\POOprod{c_3}{c_4},t)}{
		(\POOprod{c_1 \fatsemi^\ell c_3}{c_2 \fatsemi^\ell c_4},t)
	}{}
	\comprule{\POOsum{c_1}{c_2}}{(\POOsum{c_3}{c_4},t)}{
		(\POOsum{c_1 \fatsemi^\ell c_3}{c_2 \fatsemi^\ell c_4},t)
	}{}
	\comprule{m_1}{(m_2,t)}{
		(m_1,\bot^l)
	}{
		\sidecond{
		\ell = l \; \text{and} \;
		\neg m_1 \smile m_2 
		}
	}
	\end{array}
	\]

@@

We list a fraction of reduction rules due to space limitation.
When values are constructed, their hyper-coercion parts are filled with outputs 
of $ id $. For instance, when a function value is constructed, its first part 
and last part are initialized to $ id(T_1) $ and $ id(T_2) $ respectively.
When evaluating a cast expression, the current continuation is extended with a 
hyper-coercion constructed by $ cast $. $ ext $ composes the new hyper-coercion 
with the hyper-coercion on the top of the continuation.
When evaluating a compound expression, the machine firstly construct the new 
pre-continuation, then turn it to a continuation by adding an identity 
hyper-coercion at the top. For instance, when evaluating a \texttt{cons} 
expression, the machine firstly construct $ \hckOOconsI{e_2}{\rho}{\kappa} $, 
the new pre-continuation, then call $ cont $ which adds an identity cast to 
construct a continuation. 
When a function call happens, the machine firstly cast the operand. If the 
casting succeeds, the machine then evaluate the body in the extended 
environment and the extended continuation. If the casting fails, the machine 
then halts with the blame label.

>>>>

\begin{figure}
	Composition of hyper-coercions \fbox{$ c \fatsemi^\ell c = c $}
	\[ 
	\begin{array}{rclclr}

@@

	Composition of middles \fbox{$ m \fatsemi^\ell (m,t) = (m,t) $}
	\[ 
	\begin{array}{rclclr}
	\comprule{\POOunit}{(\POOunit,t)}{
		(\POOunit,t)
	}{}
	\comprule{\POOfun{c_1}{c_2}}{(\POOfun{c_3}{c_4},t)}{
		(\POOfun{c_3 \fatsemi^{\ell} c_1}{c_2 \fatsemi^\ell c_4},t)
	}{}
	\comprule{\POOprod{c_1}{c_2}}{(\POOprod{c_3}{c_4},t)}{
		(\POOprod{c_1 \fatsemi^\ell c_3}{c_2 \fatsemi^\ell c_4},t)
	}{}
	\comprule{\POOsum{c_1}{c_2}}{(\POOsum{c_3}{c_4},t)}{
		(\POOsum{c_1 \fatsemi^\ell c_3}{c_2 \fatsemi^\ell c_4},t)
	}{}
	\comprule{m_1}{(m_2,t)}{
		(m_1,\bot^l)
	}{
		\sidecond{
		\ell = l \; \text{and} \;
		\neg m_1 \smile m_2 
		}
	}
	\end{array}
	\]

@@

We list a fraction of reduction rules due to space limitation.
When values are constructed, their hyper-coercion parts are filled with outputs 
of $ id $. For instance, when a function value is constructed, its first part 
and last part are initialized to $ id(T_1) $ and $ id(T_2) $ respectively.
When evaluating a cast expression, the current continuation is extended with a 
hyper-coercion constructed by $ cast $. $ ext $ composes the new hyper-coercion 
with the hyper-coercion on the top of the continuation.
When evaluating a compound expression, the machine firstly construct the new 
pre-continuation, then turn it to a continuation by adding an identity 
hyper-coercion at the top. For instance, when evaluating a \texttt{cons} 
expression, the machine firstly construct $ \hckOOconsI{e_2}{\rho}{\kappa} $, 
the new pre-continuation, then call $ cont $, which adds an identity cast to 
form a continuation. 
When a function call happens, the machine firstly cast the operand. If the 
casting succeeds, the machine then evaluate the body in the extended 
environment and the extended continuation. If the casting fails, the machine 
then halts with the blame label.
